---
title: "Pig Personality"
author: "Noah Stetson"
date: "`r Sys.Date()`"
format: html
editor: source
---

Analyzing data on personality in pigs, using both observational and informant assessment data

Loading library
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

Loading dataset (for observational, survey, and meta data about pigs)
```{r}
# obs <- read_csv("~/Documents/GitHub/PigPersonality/obsData_30Sept.csv")
# svy <- read_csv("~/Documents/GitHub/PigPersonality/CaregiverSurveyMOCK.csv")
# meta <- read_csv("~/Documents/GitHub/PigPersonality/PigSample.csv")

obs <- obsData_30Sept
svy <- CaregiverSurveyMOCK
meta <- PigSample
```
it won't let me open files from documents, only from desktop 😳 so my working director must have been set to my desktop, but when I try to fix it it doesn't work!

Temporary fix, open copies from using base (readr)

## Cleaning Data

Change "name" in metadata to "pig" so the files can be combined
```{r}
colnames(meta) [colnames(meta) == "Name"] <- "Pig"
```

Put meta data into df based on pig
```{r}
obs_m <- inner_join(obs, meta, by = "Pig") 
```
Wait why did it change from 475 objects to 472? It deleted 2 rows?
Oh they were rows with "no value" as the pig name so they need to be omitted
