---
title: "Analysis for 26 Oct Lab Meeting"
format: html
editor: visual
---

## Loading library

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(corrr)
library(psych)
library(irr)
library(readr)
```

## Load DF

```{r}
obs <- read_csv("https://raw.githubusercontent.com/nwstetson/PigPersonality/main/Obs_Oct21_Clean.csv", show_col_types = FALSE)  # behavior observations (2/3 of the way done)

svy_current <- read_csv("~/Desktop/Dan_Oct24.csv")  # current survey data (7 responses)

meta <- read_csv("https://raw.githubusercontent.com/nwstetson/PigPersonality/main/PigSample.csv", show_col_types = FALSE) # meta data (pig demographics)
```

## Cleaning Data

Put meta data into df based on pig id number

```{r}
obs_m <- inner_join(obs, meta, by = "PigID")
current_m <- inner_join(svy_current, meta, by = "PigID")


# DF with just test items
current_svy_items <- svy_current %>% select(4:38)

# DF with just scores
current_pig_scores <- current_m %>% select(Name, 40:51)
```

### Make wide version of survey results

```{r}
current_wide <- current_m  %>% 
  pivot_longer(cols = 40:51, names_to = "facet") 
current_wide <- current_wide %>% rename_at('value', ~'facet.value')

current_wide <-current_wide %>% 
  pivot_longer(cols = 4:38, names_to = "item")

current_wide <- current_wide %>% rename_at('value', ~'item.value')
```

## Overview of survey data

### Personality Scores

```{r}
summary(current_pig_scores)

sd(current_pig_scores$SC1)
```

### Items

```{r}
summary(current_svy_items)
```

### As a table

🐽 How can I get this to average each pig's scores across raters?

```{r}
current_pig_scores <- current_m %>%
  select(Name, 40:51)

view(current_pig_scores)
```

```{r}
ggplot(current_wide, aes(x= facet, y= facet.value, group = Name, color = Name)) +
  geom_point() +
    geom_line(alpha=.5) +
    theme_classic() +
  xlab("Personality Facet") +
  ylab("Score") +
  ggtitle("Differences in Personality Scores Between Pigs")
```

## Overview of Behaviors

### As a table

🐽 How do I make a new df for observational data that does counts of each behavior

Like this:

Pig \| Behavior \| Counts

Atlas \| Sniff.obj \| 3

Atlas \| Get.disp \| 1

```{r}
behavior_table = table(obs$Pig, obs$Behavior) #Here's an overview of occurances of behaviors for now
behavior_counts <- data.frame(rbind(behavior_table)) # Don't have pig as row name


# SUmm if I save it as a CSV and reupload it it works I literally wanna die rn
# Also change "Pig" to say "name"
write.csv(behavior_counts, "~/Desktop/behavior_counts_Oct26.csv")
behavior_counts <- read_csv("~/Desktop/behavior_counts_Oct26.csv")

# Make wide version
behavior_counts_wide <-behavior_counts %>% 
  pivot_longer(cols = 2:20 , names_to = "Behavior", values_to = 'Count')


# Also make verion with meta data
behavior_m <- inner_join(behavior_counts, meta, by = "Name")
```

### As a graph

🐽 Too messy! How do I make it look like the scatterplot I did above, but with "Behavior" on x-axis

```{r}
ggplot(behavior_counts_wide, aes(x= Behavior, y= Count, group = Name, color = Name)) +
  geom_point() +
    theme_classic() +
  xlab("Behavior") +
  ylab("Counts") +
  ggtitle("Differences in Behavior Between Pigs")
```

### Sex differences in getting displaced???

Males maybeee get displaced less???

```{r}
ggplot(behavior_m, aes(x=Get.disp, fill=Sex)) + 
   theme_classic() +
  xlab("Get Displaced") +
  ylab("Counts") +
  ggtitle("How Often Do Pigs Get Displaced?") +
  geom_density(alpha = 0.4) +
  theme_minimal() +
  scale_fill_manual(values = c("#999999", "#E69F00"))
```

### Background differences in getting displaced

```{r}
ggplot(behavior_m, aes(x=Get.disp, fill=Background)) + 
  theme_classic() +
  xlab("Get Displaced") +
  ylab("Counts") +
  ggtitle("Do Pigs From Abuse/Neglect Backgrounds Get Displaced More?") +
  geom_density(alpha = 0.4) +
  theme_minimal() +
  scale_fill_manual(values = c("#999999", "#E69F00"))
```

## Internal Reliability

### Inter-item correlation

```{r}
# Make DF with just test items
current_svy_items <- svy_current %>% select(4:38)

# Overall average inter-item correlation for all surveys completed (each pig has 2 surveys)
current_svy_items_corr <- current_svy_items %>% correlate() 

view(current_svy_items_corr) # works so far

write.csv(current_svy_items_corr, "~/Desktop/Oct_26_Corr.csv") # Save as CSV and REMOVE NAS BY HAND

current_svy_items_corr <- current_svy_items_corr %>% colMeans(na.rm = TRUE) # Doesn't run because it's not numeric

 # Make it numeric
current_item_corr <- char2numeric(current_svy_items_corr)
view(current_svy_items_corr)
class(current_svy_items_corr) # Didn't make it numeric?

# Make it numeric in another way
current_svy_items_corr <- as.numeric(unlist(current_svy_items_corr)) # Messes it up
view(current_svy_items_corr) 
class(current_svy_items_corr) # Not numeric

current_svy_items_corr <- current_svy_items_corr %>% colMeans(na.rm = TRUE)
```

#### Make average correlations into a histogram

```{r}
ggplot(aes(x = current_svy_items_corr)) +
    geom_histogram(bins = 10, alpha = .5) +
    geom_vline(xintercept = mean(current_svy_items_corr), color = "dodger blue") +
    xlab("Mean inter-item correlation") +
    theme_minimal()
```

Chronbach's alpha

AHHHHH IT WON'T WORK BECAUSE DAN DIDN'T FILL OUT A QUESTION

```{r}
# psych::alpha(current_svy_items, check.keys = TRUE)

# psych::alpha(current_svy_items, check.keys = TRUE)$total$std.alpha #this just gets the alpha value itself
```

Does get.disp correlated with SC12 (dominance over pigs)

```{r}
behavior_and_scores <- inner_join(behavior_m, Pig_Scores, by = "Name")


ggplot(behavior_and_scores, aes(x=Get.disp, y=SC12)) +
         geom_point() +
          stat_smooth(method = "lm") +
    xlab("Times Displaced") +
  ylab("Dominance Score") +
  ggtitle("Do Pigs that Score Higher on Dominance Get Displaced Less?")
```

Active Engagement with Resting

```{r}
ggplot(behavior_and_scores, aes(x=Travel, y=SC9)) +
         geom_point() +
          stat_smooth(method = "lm") +
    xlab("Times Traveling") +
  ylab("Active Engagement Score") +
  ggtitle("Do Pigs that Score High on Active Engagement Travel More?")
```
